Type cones of $\b{g}$-vector fans

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex

\para{The $\b{g}$-vector fan}
%
The following statement is well known.
\vincent{Explain}

>>>>

\para{The $\b{g}$-vector fan}
%
The following statement is well known.
\vincent{Explain}
Examples are illustrated in \cref{fig:clusterFans}.

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\centerline{
	\begin{overpic}[scale=.45]{clusterFans}
	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
	\end{overpic}
	}
  \caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}
